\section{Conclusion}\label{sec:conclusion}

  % Restate the main idea of your essay, or your thesis statement
  A distributed services approach to control systems including components of
  data acquisition, data logging, and feedback control, have been presented.
  Requirements of the project included developing a message queueing system for
  inter-service communication, a RESTful API to expose features to any language
  or application capable of making basic web requests, and a plugin system that
  can be used to inject data into, and consume from, streaming services. All of
  these features were believed to reduce the amount of overhead on an
  individual host system executing any of the services, improve
  interoperability with the system from external applications, and simplify the
  development of new data sources and consumers.

  % Summarize the three subpoints of your essay
  Using ZeroMQ has shown to be an effective strategy for publishing and
  subscribing to (streaming) the data that was produced by the services within
  the system, in all test cases the networking of the host running a system was
  capable of keeping up with very high demands on the types of data produced
  while resource requirements were low. Additionally the REST APIs showed how
  it was possible to make changes to the service data models that were easy
  to test using readily available tools without needing to write client
  applications to do this. Finally, the plugin systems developed were
  demonstrated to be very effective in integrating new sources of data
  producers and consumers into the system without the overhead of recompiling
  the main code base.

  % Leave the reader with an interesting final impression
  This project has been the first steps towards a modern and heavily configurable distributed
  control system capable of delivering custom control systems with a small amount of effort,
  without having the end user need to compile any code. Efforts to find an alternative solution
  that was capable of creating these generic systems, or capable of communicating the data they
  created over any message queueing systems that are common in distributed systems revealed that
  the solution presented here is unique.
